Audio Interface of an Active Perception Navigation Aid for People with Visual Impairments

### 2019-05-20 article.tex
Added descriptions to Nicola's changes to rollback and fix a merge issue

%\begin{figure}
  %\centering
  %\includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
  %\caption{The Tango device and bone-conducting headset the system is based on. }\label{fig:tango-headphone}
%\end{figure}
\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\columnwidth}
    \includegraphics[width=1.0\columnwidth]{figures/tango_headphone.png}
    \caption{}\label{fig:tango-headphone}
  \end{subfigure}%
  ~
  \begin{subfigure}[t]{0.5\columnwidth}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/vi_participant.pdf}
    \caption{}\label{fig:participant}
  \end{subfigure}
  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and them in use in an experiment (right).}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\columnwidth]{figures/camera_coordinate.pdf}
  \caption{A diagram showing the device's frame of reference and the target's pan and tilt angles.}\label{fig:cam-coords}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=1.0\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip, trim=0 0 0 40, width=1.0\columnwidth]{figures/pitch_gain_functions.png}
  \caption{The pitch gain functions for the 3 different gain settings ($y$-axis in log scale). }\label{fig:pitch-gain}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
  \caption{Angular error data for the $m_l$ setting. }\label{fig:err-results-lo}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
  \caption{Angular error data for the $m_m$ setting. }\label{fig:err-results-med}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
  \caption{Angular error data for and the $m_h$ setting. }\label{fig:err-results-hi}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=20 -70 100 100, width=1.0\columnwidth]{figures/err_boxplot_medians.png}
  \caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=80 -70 100 0, width=1.0\columnwidth]{figures/err_boxplot_std.png}
  \caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
\end{figure}

>>>>

%\begin{figure}
  %\centering
  %\includegraphics[width=0.5\columnwidth]{figures/tango_headphone.png}
  %\caption{The Tango device and bone-conducting headset the system is based on. }\label{fig:tango-headphone}
%\end{figure}
\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\columnwidth}
    \includegraphics[width=1.0\columnwidth]{figures/tango_headphone.png}
    \caption{}\label{fig:tango-headphone}
  \end{subfigure}%
  ~
  \begin{subfigure}[t]{0.5\columnwidth}
    \centering
    \includegraphics[width=0.7\columnwidth]{figures/vi_participant.pdf}
    \caption{}\label{fig:participant}
  \end{subfigure}
  \caption{Pictures of the Tango device and bone-conducting headphones the system is based on (left) and them in use in an experiment (right).}
  \Description{A pictures of the Tango device and bone conducting headset and another of them both in-use. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\columnwidth]{figures/camera_coordinate.pdf}
  \caption{A diagram showing the device's frame of reference and the target's pan and tilt angles.}\label{fig:cam-coords}
  \Description{A diagram of the device's frame of reference. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=1.0\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }\label{fig:pipeline}
  \Description{Diagram of the system pipeline.  }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip, trim=0 0 0 40, width=1.0\columnwidth]{figures/pitch_gain_functions.png}
  \caption{The pitch gain functions for the 3 different gain settings ($y$-axis in log scale). }\label{fig:pitch-gain}
  \Description{Plots showing the 3 different pitch gradient settings. }
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_lo.png}
  \caption{Angular error data for the $m_l$ setting. }\label{fig:err-results-lo}
  \Description{Angular error results for the low setting.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_med.png}
  \caption{Angular error data for the $m_m$ setting. }\label{fig:err-results-med}
  \Description{Angular error results for the medium setting.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=450 0 450 110, width=0.8\columnwidth]{figures/err_hi.png}
  \caption{Angular error data for and the $m_h$ setting. }\label{fig:err-results-hi}
  \Description{Angular error results for the high setting.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=20 -70 100 100, width=1.0\columnwidth]{figures/err_boxplot_medians.png}
  \caption{Error medians for the pan and tilt dimension and each gradient setting.} \label{fig:err-boxplot-median}
  \Description{Angular error medians for each gradient setting. }
\end{figure}

\begin{figure}
  \centering
  \includegraphics[clip, trim=80 -70 100 0, width=1.0\columnwidth]{figures/err_boxplot_std.png}
  \caption{Error standard deviations for the pan and tilt dimensions and each gradient setting.}\label{fig:err-boxplot-std}
  \Description{Angular error standard deviations for each gradient setting. }
\end{figure}
